%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}
	\begin{center}
		\textbf{\Huge \scshape Hoang Nguyen} \\ \vspace{1pt} 
		\small 425-361-3396 $|$ \href{mailto:hoangng@uw.edu}{\underline{hoangng@uw.edu}} $|$ \href{https://github.com/kipiiler}{\underline{github.com/kipiiler}} $|$ \href{https://www.linkedin.com/in/kipiiler/}{\underline{linkedin.com/in/kipiiler}} $|$ \href{https://kipiiler.me}{\underline{kipiiler.me}}
	\end{center}


\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
			{University of Washington}{Expected Dec 2025}
			{Bachelor's in Computer Science}{}	\resumeSubHeadingListEnd


\vspace{-13pt}\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \footnotesize{\item{
     \textbf{Languages}{: Python, C++, C, Golang, SQL, Java, TypeScript} \\
     \textbf{Frameworks and Libraries}{: PyTorch, Numpy, Matplotlib, Sklearn, FastAPI, Flask, Django, CMake, vcpkg, CUDA, OpenGL, GLSL, POSIX, Gin, Postgres, Redis, MySQL, Docker, Nextjs, React, Node.js, Express.js, GraphQL, AWS, Google Cloud Platform, Spark, gRPC} \\
     
    }}
 \end{itemize}


\section{Experience}
	\resumeSubHeadingListStart

	\resumeSubheading
		{Software Engineer Intern}{Jun 2024 -- Sep 2024}
		{Visual Concepts}{Seattle, WA}
		\resumeItemListStart
			\resumeItem{Developed CUDA kernels for BVH construction by employing warp-level parallelization, which boosted build times.}
			\resumeItem{Engineered a mesh compression system by implementing custom vector quantization, which decreased 3D model memory usage by 50\%.}
			\resumeItem{Built an OpenGL + CUDA profiling tool for character rendering pipelines, which improved rendering performance analysis in NBA2K.}
		\resumeItemListEnd


	\resumeSubheading
		{Research Assistant}{Dec 2024 -- May 2025}
		{Efeslab University of Washington}{Seattle, WA}
		\resumeItemListStart
			\resumeItem{Developed GPU anomaly detection pipelines using CUDA, optimizing for 9.5\% higher F1 scores, showcasing parallel processing proficiency.}
			\resumeItem{Implemented custom DAG schedulers for efficient workload execution on consumer GPUs, enhancing resource utilization and performance.}
			\resumeItem{Utilized Python and vLLM to process 1M+ logs for cloud reliability, demonstrating AI and LLM expertise in a research context.}
		\resumeItemListEnd


	\resumeSubheading
		{Software Engineer Intern}{Oct 2023 -- Dec 2023}
		{Yoomi Health}{Remote, WA}
		\resumeItemListStart
			\resumeItem{Engineered a real-time body-pose tracking pipeline using TensorFlow.js and YOLOv5, which boosted client-side render FPS from 20 to 60, demonstrating performance optimization skills.}
			\resumeItem{Developed a custom TypeScript visualization library with 20+ charts, coupled with 95\% unit test coverage using Jest, showing proficiency in front-end development and testing methodologies.}
			\resumeItem{Built a coordinate transformation service using a custom tree structure to preprocess pose data, which reduced load time by 50\%, showcasing expertise in data processing and algorithm design.}
		\resumeItemListEnd

	\resumeSubHeadingListEnd


\section{Projects}
	\resumeSubHeadingListStart

	\resumeProjectHeading
	{\textbf{Lung Cancer Detection} $|$ \emph{Pytorch, Python, OpenCV}}{  }
	\resumeItemListStart
			\resumeItem{Developed four U-Net CNN architectures for 3D MRI image segmentation using PyTorch, which achieved 78\% accuracy on validation.}
			\resumeItem{Preprocessed and augmented a dataset of 63 MRI scans using OpenCV to improve generalization, which enhanced model robustness for lung cancer detection.}
			\resumeItem{Iterated on model design and training strategies within a team, which improved outcomes and demonstrated collaborative problem-solving skills for the federal ecosystem.}
		\resumeItemListEnd


	\resumeProjectHeading
	{\textbf{Bored Game Engine} $|$ \emph{C++, CMake, OpenGL, GLSL, ImGui, LLVM, Computer Graphics}}{  }
	\resumeItemListStart
			\resumeItem{Engineered real-time 3D rendering pipeline using OpenGL and GLSL, which improved visual fidelity and demonstrated proficiency in graphics programming.}
			\resumeItem{Designed modular game engine with ECS architecture in C++, which improved code maintainability and enabled future GPU acceleration.}
		\resumeItemListEnd


	\resumeProjectHeading
	{\textbf{Rick Sanchez Chatbot} $|$ \emph{Pytorch, Numpy, Docker, Redis, Postgres, HuggingFace, Puppeteer}}{  }
	\resumeItemListStart
			\resumeItem{Fine-tuned DialoGPT for conversational AI by implementing HuggingFace Transformers, which improved model perplexity by 12\%, demonstrating NLP expertise.}
			\resumeItem{Deployed a Discord chatbot with Docker, Redis, and Postgres, by containerizing and integrating the model, supporting state tracking and showcasing full-stack capabilities.}
		\resumeItemListEnd

	\resumeSubHeadingListEnd


\end{document}